Solent region: Test Maps

### 2021-08-05 Solent_Mapping_v2.Rmd
fixed variable name used

```{r Mapping the difference in fuel poverty from 2012 to 2018}
##BROKEN
merged_dfla$LA11CD <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla)# Merge the local Authority boundaries and the Fuel Poverty data
ggplot2::ggplot(la_merged_Fuelpov20182012dif) +
  geom_sf(aes(fill = pc_diffla)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
labs(caption="Solent (all LA)")
```

>>>>

```{r Mapping the difference in fuel poverty from 2012 to 2018}
##BROKEN
merged_dfla$LA11CD <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
ggplot2::ggplot(la_Fuelpov20182012dif) +
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
labs(caption="Solent (all LA)")
```
